---
title: "Exercise 4"
author: "Min Wang"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages and import data

First, load the packages and import the data.

```{r}
library(kableExtra)
library(dplyr)
library(quanteda) # includes functions to implement Lexicoder
library(quanteda.textmodels) # for estimating similarity and complexity measures
library(quanteda.textplots) #for visualizing text modelling results
```


```{r}
kaneko_dfm  <- readRDS(gzcon(url("https://github.com/cjbarrie/CTA-ED/blob/main/data/wordscaling/study1_kaneko.rds?raw=true")))

```


## Estimate wordfish model

Since it is already a document feature matrix, we are able to group and trim the document feature matrix before estimating the wordfish model.

```{r}
table(docvars(kaneko_dfm, "Newspaper"))
## prepare the newspaper-level document-feature matrix
# compress the document-feature matrix at the newspaper level
kaneko_dfm_study1 <- dfm_group(kaneko_dfm, groups = Newspaper)
# remove words not used by two or more newspapers
kaneko_dfm_study1 <- dfm_trim(kaneko_dfm_study1, min_docfreq = 2, docfreq_type = "count")

## size of the document-feature matrix
dim(kaneko_dfm_study1)
```

Now the Wordfish model can be estimated, using "summary" function to see the results.

```{r}
#### estimate the Wordfish model ####
set.seed(123L)
kaneko_dfm_study1_results <- textmodel_wordfish(kaneko_dfm_study1, 
                                             sparse = TRUE)

summary(kaneko_dfm_study1_results)
```


## Visualize the results

We can then plot our estimates of the $\theta$s.

```{r}
textplot_scale1d(kaneko_dfm_study1_results)
```

Plotting the "features".

```{r}
textplot_scale1d(kaneko_dfm_study1_results, margin = "features")
```

we can also look at these features.

```{r}
# extract "features" from a data structure("kaneko_dfm_study1_results") and assigns its contents to a new variable named "features1"
features1 <- kaneko_dfm_study1_results[["features"]]

# the same process as "features1"
betas1 <- kaneko_dfm_study1_results[["beta"]]

# merge "features1" and "betas1" into a new data frame called feat_betas1
feat_betas1 <- as.data.frame(cbind(features1, betas1))

# set the type of "betas1" to numeric
feat_betas1$betas1 <- as.numeric(feat_betas1$betas1)


feat_betas1 %>%
  arrange(desc(betas1)) %>%  # sort by the value of "betas1" in descending order
  top_n(20) %>%  # select the first 20 rows after sorting
  kbl() %>%   # change data frame to a table
  kable_styling(bootstrap_options = "striped") # adds a stripe style that alternates the background color of consecutive rows
```


